---
title: "Regression Analysis HW4"

date: '2020 12 6 '
output: pdf_document
---
```{r setup, include=FALSE}
library(tidyverse)
```

# 1.

a)
```{r}
load("C:/Users/admin/Downloads/dataQ1.RData")
fitted<-lm(Y~x1)
fitted
```
The fitted regression equation is
$$ \hat{Y}=40652.81-515.93\times x1 $$


b)
```{r}
summary(fitted)
```
In the summary above, we can find $$R^2=0.9734$$


c)

```{r}
par(mfrow=c(2,2))
plot(fitted)
```
We can see the pattern in first residual plot. It means the errors are autocorrelated.


d)

$$ H_0:\rho=0,\quad H_1:\rho\neq0$$

```{r}
fitted$res %>% sign() %>% factor() %>% tseries::runs.test()
```
The test statistic is -6.149 and the p-value=7.799e-10 which means it is significant under $\alpha=0.01$
Therefore we can reject $H_0$ and we can conclude the errors are autocorrelated.



e)
$$H_0: \rho=0 \quad vs \quad H_1:\rho>0$$

```{r}
lmtest::dwtest(fitted)
```
The test statistic is 0.11683 and the p-value<2.2e-16 and it means that it is significant under $\alpha=0.01$ 
Therefore we can reject $H_0$ and we can conclude the errors are positively autocorrelated.




# 2.


a)

```{r}
load("C:/Users/admin/Downloads/dataQ2.RData")
fitted_1<-lm(y~n)
fitted_1
```
The fitted regression equation is 
$$ \hat{Y}=-1.805+1.061\times n$$



b)
```{r}
plot(fitted_1$fit, scale(fitted_1$res))
```
In above plot, we can see the errors have heteroscedasticity and it violates the assumption of constancy of error variance.

c)
```{r}
fitted_2<-lm(sqrt(y)~n)
fitted_2
```


d)

The fitted regression model is
$$ \hat{\sqrt{Y}}=2.61275+0.08152\times n$$

e)
```{r}
predict(fitted_2,newdata=data.frame(n=40))^2
```


f)
```{r}
n_sq<-n^2
fitted_3<-lm(log(y)~n+n_sq)
summary(fitted_3)
```


g)
The fitted regression model in terms of the original scale is
$$\hat{Y}=exp(1.5104037+0.0674594\times n -0.0003820\times n^2)$$