---
title: "regression analysis HW2"
author: "2019150445/Shin Baek Rok"
date: '2020 10 11 '
output: pdf_document
---

# 1.

  a)
```{r}
#By matrix
x<-c(1,2,3,3,4,5,5)
y<-c(3,7,5,8,11,14,12)
X<-cbind(1,x)
coef<-solve(t(X)%*%X)%*%t(X)%*%y

coef

#By simple code
fitted<-lm(y~x)
fitted
```
By these coefficients, we can fit the regression equation.

$\hat{y_i}=0.531949+2.4468085x_i,\quad i=1,...,7$





  b)
```{r}
summary(fitted)
t<-(2.4468-2)/0.4454
1-pt(t,7-2)
```





  c)
```{r}
summary(fitted)
0.5319+(1-pt(0.25,df=5))*1.5881
0.5319-(1-pt(0.25,df=5))*1.5881
```
Therefore, 95% confidence interval is
$$ (-0,113,1.177) $$
And thus we cannot reject $H_0:\beta_0=1$ since this 95% CI contains 1.







  d)
  


```{r}
fitted1<-lm(y~1)
anova(fitted1,fitted)
```



Under $H_0$, $$SSE(RM)=\sum(y_i-\bar{y})^2=SST=93.714$$
$$SSE(FM)=\sum(y_i-\hat{y_i})^2=13.319, \quad(df=7-2=5)$$
$$SSE(RM)-SSE(FM)=93.714-13.319=80.395, \quad(df=2-1=1)$$


Therefore, $$F=\frac{80.395/1}{13.319/5}=30.18057$$

```{r}
1-pf(df1=1,df2=5,q=30.18057) #p-value of F statistic
```



  e)
  
  
  
We should find the confidence interval for the mean response $\hat{\mu_0}$ when $x_0 = 4$.

```{r}
predict(fitted, interval='confidence', newdata=data.frame(x=4),level=0.9)
```





# 2.

```{r}
mpg<-c(23,21,20,19,22,21,20,19,24,17,19)
engine<-c(3471, 2979, 4195, 4701, 3471, 3960, 4701, 4701, 3311, 4664, 4605)
hp<-c(260,225,275,235,240,195,235,265,230,235,302)
weight<-c(4420,4586,4787,4379,4439,3786,3786,3786,3860,5390,4834)
#load data

```




  a)
```{r}
lm(mpg~engine+hp+weight)

```
The fitted regression equation is 
$$\hat{mpg}=35.1805-0.026\times engine+0.0154\times hp-0.0018\times weight$$




  b)
When weight increases by one unit, 
while other variables(engine and hp) are fixed, estimated mpg decreases by 0.0018.




  c)
```{r}
full_model<-lm(mpg~engine+hp+weight)
reduced_model<-lm(mpg~1)
anova(reduced_model,full_model)
```


In anova table, F-statistic is large enough(i.e. p-value for F-statistic is small enough) to reject $H_0:\beta_1=\beta_2=\beta_3=0$.
Thus we can not ignore all variables(There is at least one significant variables).





  d)
```{r}
summary(full_model)
```


In summary of the fitted model, we can find the p-value for individual variables.
Since p-value for hp is big, we can say effect of hp variable is not significant on mpg and we may remove the hp variable from the model.
Other variables' p-values are small and we can say its' effects are significant on mpg.



  e)
```{r}
summary(lm(mpg~engine+weight))
```

And the fitted regression model is

$$\hat{mpg}=36.904-0.00237\times engine -0.00156\times weight$$





  f)
```{r}
reduced_model2<-lm(mpg~engine+weight)
anova(reduced_model2,full_model)
```


In anova between reduced model & full model, we cannot reject $H_0:\beta_2=0$ since F-statistic is small & p-value of F-statistic is quiet large.
That means the reduced model gives as good a fit as the full model.





# 3.



### g), h)
t-value=Coef/SE, thus (g)=-23.4325/12.74=-1.839286

In the same way, (h)/0.1528=8.32. Thus (h)=8.32*0.1528=1.271296 


### a), e), i), m)
It is simple linear regression, and there is 20 observations.
Thus, (i)=n(#observations)=20 , (e)=(m)=n(#observations)-p(#variables)-1=20-1-1=18,
(a)=p(#variables)=1.


### b)
(b)=MSR=SSR/p=1848.76/1=1848.76.


### c)
In SLR, $F=t_1^2=8.32^2=69.2224=(c)$


### f)
Since F=MSR/MSE=1848.76/(f)=69.2224, (f)=1848.76/69.2224=26.70754.


### d)
Since MSE=SSE/n-p-1=SSE/18=26.70754, SSE=(d)=26.70754*18=480.7357


### j)
$R^2=(j)=SSR/SST=SSR/(SSR+SSE)=1848.76/(1848.76+480.7357)=0.793631$


### k)
$R_a^2=(k)=1-\frac{SSE/18}{SST/19}=1-\frac{480.7537/18}{(1848.76+480.7537)/19}=0.7822$


### l)
$\hat\sigma=(l)=\sqrt{SSE/18}=\sqrt{480.7537/18}=5.16803$